\documentclass[10pt,letterpaper]{article}

\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage{textcomp}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=0.28in,itemsep=0pt,topsep=1pt,parsep=0pt,partopsep=0pt}

\newcommand{\resumeSection}[1]{\vspace{5pt}\begin{center}{#1}\end{center}\vspace{-2pt}}
\newcommand{\resumeEntry}[4]{\textbf{#1} -- \textit{#2}\hfill\textbf{#3}\\#4\vspace{1pt}}
\newcommand{\resumeRole}[2]{\hspace*{0.18in}\textbf{\textit{#1}}\hfill\textbf{#2}}

\begin{document}

\begin{center}
{\fontsize{14}{16}\selectfont\textbf{Julien Berman}}\\
Chevy Chase, MD \textbar{} (240) 454-2273 \textbar{} \href{mailto:julienberman@college.harvard.edu}{julienberman@college.harvard.edu}
\end{center}

\resumeSection{Education}

\resumeEntry{HARVARD UNIVERSITY}{Cambridge, MA}{May 2026}{Bachelor of Arts. Concentration: Economics.\hfill GPA: 3.93}

\resumeEntry{GEORGETOWN DAY SCHOOL}{Washington, D.C.}{May 2022}{}

\resumeSection{Research \& Writing}

\textbf{HARVARD UNIVERSITY ECONOMICS RESEARCH} -- \textit{Cambridge, MA}

\resumeRole{Professor Jesse Shapiro, Research Assistant}{March 2025 -- Present}
\begin{itemize}
  \item Analyzed data on the voting power and lending activity of international organizations to quantify changes to the increasingly fragile post-1945 liberal international order.
  \item Edited and proofed paper showing that demographic trends poorly predict election outcomes.
\end{itemize}

\resumeRole{Professor Jim Snyder, Research Assistant}{September 2024 -- Present}
\begin{itemize}
  \item Developed OCRABLE, a lightweight optical character recognition application that accurately identifies, labels, and processes both handwritten and typeset tabular data.
  \item Built a Python library, API, and website for OCRABLE to support public use.
\end{itemize}

\resumeEntry{THE HARVARD CRIMSON}{Cambridge, MA}{May 2023 -- Present}{\hspace*{0.18in}\textbf{\textit{Columns Editor and Op-ed Writer}}}
\begin{itemize}
  \item Conducted a comprehensive sentiment analysis of over 60,000 college newspaper opinion articles to measure progressive shifts in student views since 2000. (Quoted in \textit{The New York Times}.)
  \item Used patent data to quantify the effects of Trump's funding cuts to university research.
  \item Edited three student columns and one faculty column per week.
\end{itemize}

\resumeSection{Work Experience}

\resumeEntry{THE WASHINGTON POST}{Washington, D.C.}{June 2025 -- August 2025}{\hspace*{0.18in}\textbf{\textit{Editorial Intern}}}
\begin{itemize}
  \item Served as a contributing member of eight-person editorial board.
  \item Published two bylined columns and eight unsigned editorials on issues pertaining to national economic policy, including tariffs, monetary policy, and the national debt.
  \item Edited op-eds from external contributors, including policy experts and government officials.
  \item Conducted quantitative research and produced data visualizations for articles by staff columnists.
\end{itemize}

\textbf{LAWFARE @ THE BROOKINGS INSTITUTION} -- \textit{Washington, D.C.}

\resumeRole{Editorial Intern}{May 2024 -- August 2024}
\begin{itemize}
  \item Wrote long-form op-ed about the national security implications of the TikTok ban.
  \item Published document posts explaining key breaking news in the national security arena.
  \item Drafted daily and weekly newsletters and recorded podcast introductions.
\end{itemize}

\textbf{U.S. DEPARTMENT OF TREASURY} -- \textit{Washington, D.C.}

\resumeRole{Strategic Planning and Protocol Intern}{May 2023 -- August 2023}
\begin{itemize}
  \item Staffed and briefed Secretary Yellen's meetings with government officials and CEOs.
  \item Planned and advanced in-town events with principal, senior staff, press, and U.S. Secret Service.
  \item Managed Secretary Yellen's daily schedule.
\end{itemize}

\textbf{CHARLES RIVER ECONOMICS LABS} -- \textit{Cambridge, MA}

\resumeRole{President}{January 2024 -- December 2024}
\begin{itemize}
  \item Led a team of over 40 analysts, project leads, and operations directors to conduct rigorous, data-driven research for nonprofits and governmental agencies.
  \item Managed eight econometrics projects across three campuses: Harvard, Stanford, and UChicago.
  \item Developed partnerships with the EPA, UN, State Department, and others.
\end{itemize}

\resumeSection{Skills}

\textbf{TECHNICAL:} Proficient in Python, R, Java, and SQL.\\
\textbf{LANGUAGE:} Conversational French.\\
\textbf{INTERESTS:} Novel writing, violin, skiing, politics, literature.

\end{document}
