% resume_technical.tex
\documentclass[11pt,a4paper]{article}

\input{styles.tex}

\begin{document}
\Header
    {Julien Berman}
    {Chevy Chase, MD}
    {(240) 454-2273}
    {julien.d.berman@gmail.com}
\SectionHeader
    {Education}
\EducationEntry
    {Harvard University}
    {Cambridge, MA}
    {May 2026}
    [B.A. in Economics. Magna Cum Laude, highest honors in field, Phi Beta Kappa. GPA: 3.93]
\EducationEntry
    {Georgetown Day School}
    {Washington, D.C.}
    {May 2022}
\SectionHeader
    {Research}
\Entry
    {Harvard Economics Department}
    [Cambridge, MA]
    {
        \Position
            {Senior Thesis, advised by Prof. Jesse Shapiro}
            {Mar. 2025 -- Mar. 2026}
            {
                \item Showed that local newspaper coverage reduces online misinformation about vaccines and immigration.
                \item Developed novel machine learning strategy to detect misinformation at scale on Twitter.
                \item Locally served Qwen3 with vLLM to process 2.7 billion Twitter posts.
                \item Won Hoopes prize (top $70$ theses at Harvard) and Allyn A. Young prize (best economics thesis).
            }
        \Position
            {Research Assistant, Prof. Jesse Shapiro}
            {Mar. 2025 -- Dec. 2025}
            {
                \item Analyzed data on the voting power and lending activity of international organizations to quantify changes to the increasingly fragile post-1945 liberal international order.
                \item Edited and proofed paper showing that demographic trends poorly predict election outcomes.
            }
        \Position
            {Research Assistant, Prof. Jim Snyder}
            {Sep. 2024 -- May 2025}
            {
                \item Developed OCRABLE, a lightweight optical character recognition application that accurately identifies, labels, and processes both handwritten and typeset tabular data.
                \item Built a Python library, API, and website for OCRABLE to support public use.
            }
    }

\SectionHeader
    {Work Experience}
\Entry
    {The Washington Post}
    [Washington, D.C.]
    {
        \Position
            {Editorial Intern}
            {Jun. 2025 -- Aug. 2025}
            {
                \item Served as contributing member of eight-person editorial board.
                \item Published four bylined columns and ten unsigned editorials on issues pertaining to national economic policy, including tariffs, monetary policy, and the national debt.
                \item Edited op-eds from external contributors, including policy experts and government officials.
                \item Conducted quantitative research and produced data visualizations for articles by staff columnists.
            }
    }
\Entry
    {Lawfare @ The Brookings Institution}
    [Washington, D.C.]
    {
        \Position
            {Editorial Intern}
            {May 2024 -- Aug. 2024}
            {
                \item Wrote long-form op-ed about the national security implications of the TikTok ban.
                \item Published document posts explaining key breaking news in the national security arena.
                \item Drafted daily and weekly newsletters and recorded podcast introductions.
            }
    }
\Entry
    {U.S. Department of Treasury}
    [Washington, D.C.]
    {
        \Position
            {Strategic Planning \& Protocol Intern}
            {May 2023 -- Aug. 2023}
            {
                \item Staffed and briefed Secretary Yellen's meetings with government officials and CEOs.
                \item Planned and advanced in-town events with principal, senior staff, press, and U.S. Secret Service.
                \item Managed Secretary Yellen's daily schedule.
            }
    }
\Entry
    {Charles River Economics Labs}
    [Cambridge, MA]
    {
        \Position
            {President}
            {Jan. 2024 -- Dec. 2024}
            {
                \item Led a team of $40$ analysts, project leads, and operations directors to conduct rigorous, data-driven research for non-profits and governmental agencies.
                \item Managed eight econometrics projects across three campuses: Harvard, Stanford, and UChicago.
                \item Developed partnerships with the EPA, UN, State Department, and others.
            }
    }
\Entry
    {The Harvard Crimson}
    [Cambridge, MA]
    {
        \Position
            {Columns Editor \& Op-ed Writer}
            {May 2023 -- Dec. 2024}
            {
                \item Conducted a comprehensive sentiment analysis of over $60,000$ college newspaper opinion articles to measure progressive shifts in student views since 2000. (Quoted in The New York Times.)
                \item Used patent data to quantify the effects of Trump's funding cuts to university research.
                \item Edited three student columns and one faculty column per week.
            }
    }
\SectionHeader
    {Skills}
\SkillEntry
    {Technical}
    {Proficient in Python, R, PyTorch, scikit-learn, pandas, dask, and vLLM.}
\SkillEntry
    {Language}
    {Conversational French.}
\SkillEntry
    {Interests}
    {Novel Writing, violin, skiing, politics, literature.}
\end{document}

